\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-21 WOOT/Files/badusb.tex
remove of mode comparison, fix effective table
Figures
Some comments about figures
impl revision

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. In this section, we first introduce the hardware components we used to build \tool, then we focus on the three different attack modes we implement  for various scenario. The comparison of these modes is available at Table~\ref{table:mode_comparison}
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Mode & Detectibility & Automation & Power Consumption  \\
	\hline
	Scripting & Medium & Yes & Low\\
	\hline
	Remote Control & High & No & High \\
	\hline
	Privacy Extraction & Low & Yes & Medium\\
	\hline
	\end{tabular}
	\linebreak
	\caption{Comparison of Different Mode}
	\label{table:mode_comparison}
\end{table*}

\subsubsection{Attack Model}
The components in our attack model are as follows and the relation between them is illustrated at Fig.~\ref{fig:attack_model}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
	\item\textit{HID Emulator} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
\end{itemize}
\begin{figure}[hbtp]
	\includegraphics[width=\linewidth]{./Figs/attack_model.png}
	\caption{Attack Model}
	\label{fig:attack_model}
\end{figure}
\textbf{Scripting Mode}
\tool under this mode works almost the same like the original Rubber Ducky with various improvement.

First \tool supports defense mechanism bypass. As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack. But such defense mechanism needs visual notification to request authentication for unknown USB device. This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it automatically or manually. After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.

As the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky. Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation. This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario. Details can be obtained in Section~\ref{sec:experiment}.

@@

\textbf{Remote Control Mode}
In \tool, we implement all components required to operate a computer/mobile remotely, including a video stream, keyboard/mouse emulation.

@@

\textbf{Privacy Extraction Mode}
\tool under this mode does not emulate other USB device and solely rely on the video stream function of USB 3.x.

When running in this mode, \tool passively process the victim's video stream and detect for ``valuable'' private data.  Here, a data is ``valuable'' or not is decided by a customized detector, we implement a simple one of payment code for demonstration purpose. Though this detector is simple to implement, we successfully transfer money from the victim. More detail can be obtained in Section~\ref{sec:experiment}.

Though \tool under this mode is least detectable, \tool is also unable to fetch any information actively. All the video stream has to be analyzed and filtered to become usable private information.

>>>>

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. In this section, we first introduce the hardware components we used to build \tool, then we focus on the three different attack modes we implement  for various scenario.

\subsubsection{Attack Model}
The components in our attack model are as follows and the relation between them is illustrated at Fig.~\ref{fig:attack_model}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by embedded computer.
	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
	\item\textit{HID Emulator} emulates HID device which can be controlled from either the embedded computer.
\end{itemize}
\begin{figure}[t]
	\centering
	\includegraphics[width=0.75\linewidth]{./Figs/attack_model.png}
	\caption{Attack Model}\shuqing{Need to be more compact.}
	\label{fig:attack_model}
\end{figure}
\textbf{Scripting Mode} This mode majorly relies on the ``HID Emulator'' to send constructed HID packet to the victim. These constructed HID packet will be interpreted by the victim as valid key strokes and mouse moves. Thus the attacker can executes arbitrary scripts on the victim's device. This is the function of the original BadUSB. Based on this, we made the following improvement.

First \tool supports defense mechanism bypass. As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack. But such defense mechanism needs visual notification to request authentication for unknown USB device. This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it. After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.

Moreover, as the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky. Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation. This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario. Details can be obtained in Section~\ref{sec:experiment}.

@@

\textbf{Privacy Extraction Mode}
\tool under this mode does not emulate other USB device and solely relies on the video stream function of USB 3.x and use ``Video Capture'' component to deliver the stream to the embedded computer. The victim's device will mistakenly treat \tool as a external monitor and try to output its video stream. This stream is latter processed by the embedded computer to extract private data.

When running in this mode, \tool passively process the victim's video stream and detect for ``valuable'' private data.  Here, a data is ``valuable'' or not is decided by a customized detector, we implement a simple payment code detector for demonstration purpose. Though this detector is simple to implement, we successfully transfer money from the victim. More detail can be obtained in Section~\ref{sec:experiment}.

\textbf{Remote Control Mode}
In \tool, we have implemented all components required to control a computer/mobile remotely, including a video stream, keyboard/mouse emulation. Thus with all components enabled, not only will the victim's device treat \tool as a external display, but also a valid HID input source. Hence we can archive complete hijack of victim's device.

@@
